Gas exchange in large rivers influenced by largest turbulent eddies: implications for remotely sensing gas exchange via the SWOT satellite

### 2021-10-01 manuscript_v5.Rmd
revalidation of biker using chainsaw model

In this context, here we borrow tools from fluvial geomorphology and revist the fundamental mechanisms behind gas exchange in large rivers to answer the following question: does the small-eddy model work in large rivers like those that SWOT will observe? We exploit the findings from this analysis to develop a novel methodology that predicts $k_{600}$ (*k* normalized to a Schmidt number of 600) and its explicit uncertainity solely using SWOT observations. The method requires no in situ inputs of any kind (although in situ data can be ingested and will improve results). We name the RS of $k_{600}$ algorithm BIKER, or the 'Bayesian Inference/Inversion of the $k_{600}$ Evasion Rate' and validate it for 47 SWOT-observable rivers from around the world using hydraulic models to produce SWOT-like data (as SWOT has not yet launched). We also quantify BIKER's sensitivity to the expected SWOT measurement errors on 17 of those rivers: while SWOT data represent a sea change in inland water monitoring, it is expected to have an approximately 10cm error in water surface elevation [@biancamariaSWOTMissionIts2016] as well as river width errors [@frassonExploringFactorsControlling2021]. Finally, we use previously published dissolved $CO_2$ data to represent a hypothetical in situ $CO_2$ sensor and compare the bulk carbon efflux from the 47 rivers as calculated using BIKER and previously published in situ techniques for predicting $k_{600}$.

@@

We validate BIKER on 47 SWOT-simulated rivers using daily observed hydraulics and the metrics described in Table S2. We also re-validate BIKER on the 17 rivers with the SWOT error model which corrupts the river width and slope. Regardless of the validation setup, we do not have observed $k_{600}$ data for these rivers, and to our knowledge no field dataset of $k_{600}$ exists in the type of temporal and spatial frequency that SWOT (and therefore the BIKER algorithm) provides. Therefore, we take the model outlined in equation 4 and Figure 3 and use that to calculate the observed $k_{600}$ that BIKER is validated against. This is why equation 3's $\beta$ is trated as known and not a parameter. With this setup, we are directly exploring BIKER's ability to infer observed $A_0$ and $k_{600}$ from *W* and *H* alone, as the *k* scaling model has already been sucessfully validated (Figure 3). This workflow is elaborated on in Text S3.

>>>>

In this context, here we borrow tools from fluvial geomorphology and revist the fundamental mechanisms behind gas exchange in large rivers to answer the following question: does the small-eddy model work in large rivers like those that SWOT will observe? We exploit the findings from this analysis to develop a novel methodology that predicts $k_{600}$ (*k* normalized to a Schmidt number of 600) and its explicit uncertainity solely using SWOT observations. The method requires no in situ inputs of any kind (although in situ data can be ingested and will improve results). We name the RS of $k_{600}$ algorithm BIKER, or the 'Bayesian Inference/Inversion of the $k_{600}$ Evasion Rate' and validate it for 47 SWOT-observable rivers from around the world using hydraulic models to produce SWOT-like data (as SWOT has not yet launched). We also quantify BIKER's sensitivity to the expected SWOT measurement errors on 16 of those rivers: while SWOT data represent a sea change in inland water monitoring, it is expected to have an approximately 10cm error in water surface elevation [@biancamariaSWOTMissionIts2016] as well as river width errors [@frassonExploringFactorsControlling2021]. Finally, we use previously published dissolved $CO_2$ data to represent a hypothetical in situ $CO_2$ sensor and compare the bulk carbon efflux from the 47 rivers as calculated using BIKER and previously published in situ techniques for predicting $k_{600}$.

@@

We validate BIKER on 47 SWOT-simulated rivers using daily observed hydraulics and the metrics described in Table S2. We also re-validate BIKER on the 16 rivers with the SWOT error model which corrupts the river width and slope. Regardless of the validation setup, we do not have observed $k_{600}$ data for these rivers, and to our knowledge no field dataset of $k_{600}$ exists in the type of temporal and spatial frequency that SWOT (and therefore the BIKER algorithm) provides. Therefore, we take the model outlined in equation 4 and Figure 3 and use that to calculate the observed $k_{600}$ that BIKER is validated against. This is why equation 3's $\beta$ is trated as known and not a parameter. With this setup, we are directly exploring BIKER's ability to infer observed $A_0$ and $k_{600}$ from *W* and *H* alone, as the *k* scaling model has already been sucessfully validated (Figure 3). This workflow is elaborated on in Text S3.
